% author: Jeremy Kun
\documentclass[11pt]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}

% title metadata
\firstname{Nikola}
\familyname{Henezi}
\email{nikola@henezi.com}
\homepage{nikola.henezi.com}

\definecolor{MidnightBlue}{rgb}{0.1, .35, .65}

\begin{document}
	\maketitle
  \section{What did I do? {\color{gray}\scriptsize{- latest projects}}}
  \cventry{\httplinku[Mozilla]{www.mozilla.org}}
  {}{}{}
					{
            \httplinku[Mozilla Rep]{https://reps.mozilla.org/u/nikola/},
            \httplinku[Mozillian]{https://mozillians.org/en-US/u/nikolah/},
            member of the local community responsible for website, organization of
            Firefox OS related events and developer talks. Contributor since
            2013 (MDN, Gaia)
          }
          {- Mozilla Developer Network, Gaia, Firefox OS}

			\cventry{\httplinku[Neutrino]{http://neutrinodev.com/}}
					{} {} {}
					{Neutrino is a small development studio based in Zagreb, Croatia.
            Developed numerous social data mining tools and proxy to social API
          with prioritization, caching and token distribution}
        {- data mining, load balancing, Social API}
			\cventry{\httplinku[Buildercore]{http://buildercore.com}}
					{} {} {}
          {Buildercore is a cloud-based sales management solution for medium
            and highrise real estate developers. Developed complex multi-site
            angular.js architecture}
					{- angular.js, jade, less, nginx}
			\cventry{Q4U}
					{} {} {}
          {Q4U is a fun and fast game where you can meet someone new. Focused
            on "breaking the ice" problem. Co-founder, backend developer,
            sysadmin/DevOps, statistician and everything else that comes with a
          startup}
					{- matching algorithms, real-time game and chat}
      \cventry{\httplinku[Ultimate Tic-Tac-Toe]{ultimatetct.com}}
      {}{}{}
      {Ultimate Tic-Tac-Toe is a 2 player board game similar to Tic-Tac-Toe.
        You are playing 10 Tic-Tac-Toe game simultaneously on one 9x9 board.
        Still in development}
      {- artificial intelligence and machine learning}
      \cventry{\httplinku[Feedback.guru]{feedbackguru.foo.com.hr}}
      {}{}{}
      {
        Feedback Guru is a platform for customers to easily and anonymously provide
        feedback to companies. It was started during a hackaton and it’s still in alpha phase}
      {- real time feedbacks, semantic analysys for feedbacks and analytics}
      \cventry{Freelancer}
      {}{}{}
      {
      A freelance developer for past 5 years; built numerous sites, contributed to
      open-source projects, wrote many scripts and worked with numerous technolo-
      gies}{}




	\section{Experienced in? {\color{gray}\scriptsize{- only a small subset of
        everything I've worked with}}}
		\cvline{Javascript}{Reflux.js, React.js, angular.js, node.js, socket.io}
    \cvline{Python}{Cherrypy, scipy, sage, Flask, Django, SqlAlchemy}
    \cvline{PHP}{Laravel, Yii}
    \cvline{GNU/Linux}{Only GUI I use regularly is a web browser}
    \cvline{Databases}{MySql, Postgres, Redis, MongoDB}
    \cvline{Haskell}{Yesod}
    \cvline{Math}{Category theory, $\lambda$ calculus, logic, and many, many more
    things}
    \cvline{Computer Science}{AI, PLT, machine learning, compilers, etc.}

	\section{Formal education}
		\cventry{2014 - present}
				{Computer Science and mathematics, }
				{Department of Mathematics, Faculty of Zagreb, University of Zagreb}
				{Zagreb}{Croatia}
				{Graduate study, Thesis: Closed Cartesian Categories (CCC) and typed
          lambda calculus (in progress)}

		\cventry{2010 - 2014}
				{Mathematics, }
				{Department of Mathematics, Faculty of Zagreb, University of Zagreb}
				{Zagreb}{Croatia}
				{Undergraduate study}

  \section{Notable events I've been part of}
    \cvline{Mozilla Festival}{\httplinku{mozillafestival.org}}
    \cvline{DORS/CLUC}{\httplinku{www.dorscluc.org} - Croatian Linux user convention.}
    \cvline{NSND}{\httplinku{www.nsnd.org}}
    \cvline{Mobile App Camp}{\httplinku{www.mobileappcamp.org}}
    \cvline{Eleven selections days}{\httplinku{eleven.bg} - invited to selections days}
    \cvline{Aaron Swartz memorial hackaton}{\httplinku[Organized memorial
      hackaton in Zagreb]{bit.ly/1Hjtpco}}

  \section{Talks}
    \cvline{COQ}{Held lectures in \httplinku[Hacklab in mama]{hackerspaces.org/wiki/Hacklab_in_mama} based on \httplinku[Software foundations]{www.cis.upenn.edu/~bcpierce/sf/}, a book by Benjamin C. Pierce, in COQ [\httplinku{coq.inria.fr}].}

	\section{Foreign Languages}
		\cvlanguage{English}{Fluent}{}
		\cvlanguage{German}{Basic}{}

	\section{Interests}
		\cvline{Music}{\small I dabble with many instruments, including the guitar, piano  and harmonica.}
    \cvline{Traveling}{Backpacked most of the Europe.}
    \cvline{UI/UX design}{\small I'm very interested in UI/UX design and semantic web.}
    \cvline{Free software}{\small GNU/Linux and free software
      enthusiast/supporter. Member of the EFF}
    \cvline{Skill sharing}{\small Part of a skill sharing program held in \httplinku[Hacklab in mama]{hackerspaces.org/wiki/Hacklab_in_mama}.}

\end{document}
